Centers and centralizers of higher enveloping algebras of Lie algebras

### 2020-09-09 draft.tex
edits in section on calculus

\begin{thm}
\label{thm: centralizer}
Let $\fg$ and $\fh$ be $L_\infty$ algebras over the real or complex numbers, 
and let $f: \fg \rightsquigarrow \fh$ be a homotopy-coherent morphism of $L_\infty$ algebras
(i.e., a map of conilpotent cocommutative coalgebras $f: \cliels(\fg) \to \cliels(\fh)$).
This map determines functorially a map of $\EE_n$ algebras
\[
\UU_n f: \UU_n \fg \to \UU_n \fh
\]
between their enveloping $\EE_n$ algebras.
The centralizer of this map ${\frak Z}_n(\UU_n f)$ is an $\EE_n$-algebra modeled by the factorization algebra 
\[
\clies(\Omega^* \otimes \fg, \cliels(\Omega^*_c \otimes \fh)_f)
\]
equipped with a convolution-type product,
where the subscript $f$ indicates how $\cliels(\Omega^*_c \otimes \fh)$ is a module over $\Omega^* \otimes \fg$.
\end{thm}

@@

\owen{I think we could (and maybe should) also discuss the $\EE_n$-Koszul dual situation involving cochains.}

@@

\greg{Somewhere we should recall that $\UU_n$ and its center are unoriented $\EE_n$-algebras and define factorization algebras over any manifold that came from the formula}

@@

A ${\rm Disk}^\sqcup_M$-algebra $A$ is {\em locally constant} if for any embedding of disks $D \hookrightarrow D'$ in $M$ that the induced map $A(D) \to A(D')$ is an equivalence. 
When $M = \RR^n$, it is a result of Lurie that the theory of locally constant ${\rm Disk}^\sqcup_n$-algebras is equivalent to the theory of $\EE_n$-algebras.

@@

A prefactorization algebra is a {\em factorization} algebra if it satisfies a certain codescent condition, see Section 5.5.4 of \cite{LurieHA} or Chapter 6 \cite{CG1}. 
Locally constant factorization algebras provide another model for $\EE_n$-algebras: there is an equivalence of $\infty$-categories between locally constant factorization algebras on $\RR^n$ and $\EE_n$-algebras.

Throughout the text, we will refer to particular strict factorization (or strict ${\rm Disk}^\sqcup_M$) algebras using bold fonts, e.g. $\bU, \bZ$, etc.. 
The homotopy coherent $\EE_n$-algebras will be denoted by blackboard font, e.g. $\UU$, except for the centralizer of a map where we will use the symbol $\fZ(f)$.

@@

\begin{rmk}
It follows from theorem~\ref{T:UnofLie} that for any $\EE_n$-algebra $B$, 
its underlying complex is equipped with a homotopy-coherent Lie algebra structure.
Depending on one's preferences, one can work with an an $L_\infty$-algebra structure or strictify to a dg Lie algebra structure (at the cost of replacing the complex with something quasi-isomorphic but typically much larger).
\end{rmk}

@@

The notation $\int_{S^{n-1}}\UU_n\fg$ produces a factorization algebra on $\RR$.
Indeed,
\begin{align*}
\int_{S^{n-1}}\UU_n\fg 
&\simeq \cliels(\Omega^*_c(\RR_{> 0} \times S^{n-1}) \otimes \fg)\\
&\simeq \cliels(\Omega^*_c(\RR_{> 0}) \otimes H^*(S^{n-1}) \otimes \fg)
\end{align*}
because $(n-1)$-sphere is formal over the rationals (or reals). 
We thus see that 
\[
\int_{S^{n-1}}\UU_n\fg \simeq \UU_1 (H^*(S^{n-1}) \otimes \fg)
\]
The cohomology of the $(n-1)$-sphere is 
\[
R_n = k[\epsilon_{n-1}]/(\epsilon_{n-1}^2),
\] 
where $|\epsilon_{n-1}| = n-1$.
Since $\UU_1 (H^*(S^{n-1}) \otimes \fg)$ is manifestly equivalent to the dg algebra~$U(\fg \otimes R_n)$,
we find that 
\[
\int_{S^{n-1}}\UU_n\fg \simeq U(\fg \otimes R_n)
\]
as $E_1$ algebras.

Recall from Section~\ref{sec: enveloping} that $\UU_n \fg$ admits two convenient models:
as a factorization algebra by $\bU_n \fg$ and as a strict algebra over a colored operad $\Disk_n$ assigning $\Sym(\fg[1-n])$ to each disk.
For $n > 1$ that is a commutative algebra.
\owen{Should I say that??? And should we remark that the $n=1$ case is known???}

@@

We also know that for an abelian dg Lie algebra~${\frak a}$, 
\[
\cliels({\frak a}) = \Sym({\frak a}[1])
\]
and hence provides a free dg commutative algebra.
This feature can be leveraged to prove the following result about $\EE_n$-centers of free commutative algebras.

@@

\owen{If I'm understanding, this section shows that our construction satisfies the ``composition'' of centralizers on the nose. One corollary is that the center has a strict associative product!}

The universal property of centralizer (recall definition~\ref{D:centralizer}) implies that 
for any maps $A\stackrel{f}\to B$ and $B\stackrel{g}\to C$ of $\EE_n$-algebras, 
there is a natural map of $\EE_n$-algebras
\begin{equation}
\label{eqdef:canonicaltocentralizers} 
{\frak Z}_n(g) \otimes {\frak Z}_n(f) \longrightarrow {\frak Z}_n(g\circ f)
\end{equation}
that arises from following commutative diagram of $\EE_n$-algebras:
\[
\begin{tikzcd}
&   {\frak Z}_n(g) \otimes  {\frak Z}_n(f) \otimes A \arrow[rr, "\id\otimes \ev_f"] &&  {\frak Z}_n(g) \otimes  B \arrow[dr, "\ev_g"]\\
A \arrow[ur, "1\otimes \id_A"] \arrow[rr, "f"] && B \arrow[rr, "g"] \arrow[ur, "1\otimes \id_B"] && C 
\end{tikzcd}.
\]
When $f=g=\id_A:A\to A$, we thus obtain a canonical morphism 
\begin{equation} 
\label{eq:dgAssofcenter}
{\frak Z}_n(A){\otimes} {\frak Z}_n(A) \longrightarrow {\frak Z}_n(A).
\end{equation}
Lurie \cite{HA} has proved that this multiplication makes the center into an $E_1$ algebra in $\EE_n$-algebras 
and therefore an $E_{n+1}$-algebra, by Dunn additivity. 
%To be precise, there is the following result.
%
%\begin{prp}[\cite{LurieHA} Section 5] 
%\label{P:PtyCenter}
%\begin{itemize}
% \item The canonical map~\eqref{eq:dgAssofcenter} makes the center ${\frak Z}_n(A)$ into an $E_1$-algebra in the symmetric monoidal category of 
% $\EE_n$-algebras.
% \item There is a canonical equivalence of the $\infty$-category $E_1\mathrm{-Alg}(\EE_n\mathrm{-Alg})$ with $E_{n+1}\mathrm{-Alg}$.
%\end{itemize}
%\end{prp}

@@

The $\EE_n$-center, or $\EE_n$-Hochschild cohomology, of an $\EE_n$-algebra $A$ is the {\em universal} $E_{n+1}$-algebra that acts on $A$ {\em qua} $\EE_n$ algebra.

In Section \ref{sec:swiss} below, we will recall an elegant operadic articulation of this idea and rephrase it in terms of {\em constructible factorization algebras} on a half-space~$\HH^{n+1}$.

\owen{Mention lots of prior work, e.g., Greg et al, Ayala-Francis, Geoffroy Horel, and so on}

%
%\brian{HKR}
%
%Consider the case $n=1$ and $B = U \fg$ where $f$ is simply the identity map. 
%A classic result of \cite{HochSerre} is that the Hochschild cohomology of $U \fg$ can be expressed in terms of Lie algebra cohomology as $\Hoch^*(U\fg,U\fg) \simeq \clies(\fg, U\fg^{ad})$. 
%On the right-hand side, we take the Chevalley--Eilenberg cochain complex with values in the module $U \fg$ equipped with the adjoint action.
%The algebra structure is given by a special case of the convolution product as in Section \ref{??}. 
%
%On the other hand, our model for the derived center ${\frak Z}(U(\fg))$ of $U \fg$ is the one-dimensional factorization algebra assigning the cochain complex
%\[
%\clies(\fg \otimes \Omega^*(U), \cliels( \fg \otimes \Omega^*_c(U)))
%\]
%to each open set $U \subset \RR$.
%In the case that $U$ is an interval, this cochain complex is quasi-isomorphic to $\clies (\fg , U\fg^{ad})$.
%Furthermore, one can verify that the resulting $E_1$-algebra structure agrees with the one coming from convolution. 
%
%Our model also gives us a simple description of the factorization homology of the derived center along the circle $S^1$.
%\[
%\int_{S^1} {\frak Z}(U(\fg)) \simeq \clies(\fg[\epsilon], \cliels( \fg[\epsilon])),
%\]
%where $\epsilon$ is a formal variable of degree~$1$. 
%\brian{We should compare with Tamarkin-Tsygan's noncommutative calculus (cf. section 2.6).
%We could exhibit Theorem 2.7.1 explicitly in this case for the $\EE_n$ case with enveloping algebras.}

@@

The operad of little $n$-disks is built from configurations of disjoint unions of $n$-disks inside $n$-dimensional Euclidean space.
The $(n+1)$-dimensional Swiss cheese operad is a two-colored operad whose algebras include pairs $(B, M)$ where $B$ is an $\EE_{n+1}$-algebra, $M$ is an $\EE_n$-algebra, and where $M$ is a left-module for $B$.

@@

\begin{qtn}
Is the canonical map \eqref{eqn: can cen int} a weak equivalence when $\UU_n \fg$ is replaced by an arbitrary $\EE_n$-algebra?
\end{qtn}

\owen{We should see if that's what Tamarkin-Tsygan prove for  $E_1$ algebras, as it would be further evidence.}

@@

\owen{Then ask what is the factorization homology on a compact manifold with boundary, which leads into next section.}

@@

\section{Centers and topological field theories}
\label{sec: TFT}
%
%Given an $E_{n+1}$-algebra one can speak of its $\infty$-category of left (or right) modules.
%This is obtained by ``forgetting" the $E_{n+1}$-algebra to an $E_1$-algebra then considering the left-modules for this $E_1$-algebra.
%
%The $\EE_n$-center, or $\EE_n$-Hochschild cohomology, of an $\EE_n$-algebra $A$ is the {\em universal} $E_{n+1}$-algebra which acts on $A$. 
%In Section \ref{sec:swiss} below, we will recall an elegant operadic interpretation of this universal picture and interpret it in terms of {\em constructible factorization algebras}. 
%In the case of $\EE_n$-enveloping algebras, we will provide a strict factorization model of this universal situation in terms of a constructible factorization algebra on an $(n+1)$-dimensional 
%manifold with boundary. 
%
%We will furthermore provide an interpretation of this constructible factorization algebra in terms of the quantization of a certain topological field theory. 
%The key insight is that there is a {\em classical limit} of the $\EE_n$-center $\fZ_n(\fg)$ which is equivalent to the observables of an $(n+1)$-dimensional topological field theory known as {\em BF theory}. 
%Likewise, there is a classical limit of $\UU_n(\fg)$ which can be viewed as a boundary condition for BF theory.
%
%In this sense, topological BF theory is the universal $(n+1)$-dimensional field theory which has the $\EE_n$-enveloping algebra as a boundary condition. 
%This partially confirms the terminology used in \cite{ButsonYoo}  of topological BF theory as the ``universal bulk theory" of $\UU_n(\fg)$.

In this section, we turn to an interpretation of the $\EE_n$-center of an $\EE_n$-enveloping algebra in terms of a certain topological field theory (TFT).

Given an $\EE_n$-algebra $A$, the pair $(\fZ_n (A) , A)$ is an algebra over the $(n+1)$-dimensional Swiss cheese operad. 
The first objective is to define a certain ``classical limit" of this pair in the case that $A$ is an $\EE_n$-enveloping algebra.

@@

The key insight is that there exists a filtration on our model $\bZ_n(\fg)$ for the $\EE_n$-center and our model $\bU_n (\fg)$ for the $\EE_n$-enveloping algebra  whose associated graded factorization algebras ${\rm Gr} \; \bZ_n(\fg)$ and ${\rm Gr} \; \bU_n(\fg)$ are commutative factorization algebras.

Given a filtered associative algebra whose associated graded is commutative, there exists a Poisson bracket on the associated graded algebra. 
If the associated graded of a filtered $\EE_n$-algebra is commutative, then it carries the structure of a $\PP_n$-algebra, which is similar to a Poisson algebra except the bracket is of cohomological degree $1-n$. 
There is a similar description of the ``classical limit"  of algebras over the $(n+1)$-dimensional Swiss cheese operad in terms of algebras over a certain two-colored operad $\PP_{[n+1,n]}$, introduced by Safronov \cite{Pavel1, Pavel2}, whose definition we recall below.

@@

In the previous section, we mentioned another geometric model for algebras over the $(n+1)$-dimensional Swiss cheese operad in terms of constructible factorization algebras on $(n+1)$-manifolds with boundary.
One drawback of the previous section is that we did not provide a model of this type for the $\EE_n$-center of an enveloping algebra. 
The next goal of this section is to provide a model of the classical limit of the $\EE_n$-center as a constructible factorization algebra.

@@

%Let $\fg$ be a dg Lie algebra and consider the $\EE_n$ algebra $\UU_n \fg$. 
%We have shown that a model for the $\EE_n$-center ${\frak Z}_n (\UU_n \fg) = {\frak Z}_n ({\rm id}_{\UU_n \fg})$ is the $n$-dimensional locally constant factorization algebra 
%\[
%\clie \left( \fg \otimes \Omega \; , \; \clieu (\fg \otimes \Omega_c) \right)  .
%\]

@@

We prove Proposition \ref{prp:swiss1} by exhibiting a filtration at the level of strict factorization algebras in our model of the $\EE_n$-center.

@@

Consider our factorization model for the $\EE_n$-enveloping algebra $\bU_n(\fg) = \cliels (\fg \otimes \Omega^\bu_c)$. 
The filtration on Chevalley--Eilenberg chains equips $\bU_n(\fg)$ with a filtration as a factorization algebra.

There is a similar filtration on our model for the $\EE_n$-center $\bZ_n(\fg)$ defined by
\[
F^k \bZ_n(\fg) = \clies \bigg(\fg \otimes \Omega \; , \; \clieu_{\leq k} (\fg \otimes \Omega_c) \bigg) .
\]

@@

We turn towards a model for the $\EE_n$-center as a constructible factorization algebra.

@@

In this section, we describe a relationship between our model of the $\EE_n$-center and a certain topological field theory. 
This theory admits a natural description via the AKSZ formalism \cite{AKSZ}, which we briefly recount now.

@@

The main result of this section is that the classical observables are equivalent to our constructible model for the classical limit of the $\EE_n$-center.

@@

\def \Fac {\mathrm{Fac}}
We now need to express the $\EE_n$-structure on ${\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n\fg}}(\UU_n \fg, B_f)$ induced by the equivalence of Proposition~\ref{P:ModentoModSn}, and then on the subsequent isomorphic hom spaces of modules morphisms.  Since we are going to take advantage of the factorization algebra presentation of $\UU_n( \fg)$, see~Theorem~\ref{T:UnofLie}, we recall the following factorization algebra description of the centralizer.
Let $\cA \stackrel{f}\to \cB$ be a morphism of locally constant factorization algebras on $\RR^n$ corresponding to an $\EE_n$-algebra map similarly denoted. Then by Theorems~\ref{thm:lurie1}, \ref{T:centralizer=inthom} the centralizer of $f$ is represented by the locally constant factorization algebra  
${\rm Mor}_{\Fac_{\cA}}(\cA, \cB_f)$ which is the internal mapping object  of maps from $\cA$ to $\cB_f$ in the $\infty$-category of locally constant factorization algebras on $\RR^n$ which are a $\cA$-module.

>>>>

\begin{thm}
\label{thm: centralizer}
Let $\fg$ and $\fh$ be $L_\infty$ algebras over the real or complex numbers, 
and let $f: \fg \rightsquigarrow \fh$ be a homotopy-coherent morphism of $L_\infty$ algebras
(i.e., a map of conilpotent cocommutative coalgebras $f: \cliels(\fg) \to \cliels(\fh)$).
This map determines functorially a map of $\EE_n$ algebras
\[
\UU_n f: \UU_n \fg \to \UU_n \fh
\]
between their enveloping $\EE_n$ algebras.
The centralizer of this map ${\frak Z}_n(\UU_n f)$ is an $\EE_n$ algebra modeled by the factorization algebra 
\[
\clies(\Omega^* \otimes \fg, \cliels(\Omega^*_c \otimes \fh)_f)
\]
equipped with a convolution-type product,
where the subscript $f$ indicates how $\cliels(\Omega^*_c \otimes \fh)$ is a module over $\Omega^* \otimes \fg$.
\end{thm}

@@

\owen{I think we could (and maybe should) also discuss the $\EE_n$ Koszul dual situation involving cochains.}

@@

\greg{Somewhere we should recall that $\UU_n$ and its center are unoriented $\EE_n$ algebras and define factorization algebras over any manifold that came from the formula}

@@

A ${\rm Disk}^\sqcup_M$-algebra $A$ is {\em locally constant} if for any embedding of disks $D \hookrightarrow D'$ in $M$ that the induced map $A(D) \to A(D')$ is an equivalence. 
When $M = \RR^n$, it is a result of Lurie that the theory of locally constant ${\rm Disk}^\sqcup_n$-algebras is equivalent to the theory of $\EE_n$ algebras.

@@

A prefactorization algebra is a {\em factorization} algebra if it satisfies a certain codescent condition, see Section 5.5.4 of \cite{LurieHA} or Chapter 6 \cite{CG1}. 
Locally constant factorization algebras provide another model for $\EE_n$ algebras: there is an equivalence of $\infty$-categories between locally constant factorization algebras on $\RR^n$ and $\EE_n$ algebras.

Throughout the text, we will refer to particular strict factorization (or strict ${\rm Disk}^\sqcup_M$) algebras using bold fonts, e.g. $\bU, \bZ$, etc.. 
The homotopy coherent $\EE_n$ algebras will be denoted by blackboard font, e.g. $\UU$, except for the centralizer of a map where we will use the symbol $\fZ(f)$.

@@

\begin{rmk}
It follows from theorem~\ref{T:UnofLie} that for any $\EE_n$ algebra $B$, 
its underlying complex is equipped with a homotopy-coherent Lie algebra structure.
Depending on one's preferences, one can work with an an $L_\infty$-algebra structure or strictify to a dg Lie algebra structure (at the cost of replacing the complex with something quasi-isomorphic but typically much larger).
\end{rmk}

@@

The notation $\int_{S^{n-1}}\UU_n\fg$ produces a factorization algebra on $\RR$.
Indeed,
\begin{align*}
\int_{S^{n-1}}\UU_n\fg 
&\simeq \cliels(\Omega^*_c(\RR_{> 0} \times S^{n-1}) \otimes \fg)\\
&\simeq \cliels(\Omega^*_c(\RR_{> 0}) \otimes H^*(S^{n-1}) \otimes \fg)
\end{align*}
because $(n-1)$-sphere is formal over the rationals (or reals). 
We thus see that 
\[
\int_{S^{n-1}}\UU_n\fg \simeq \UU_1 (H^*(S^{n-1}) \otimes \fg)
\]
The cohomology of the $(n-1)$-sphere is 
\[
R_n = k[\epsilon_{n-1}]/(\epsilon_{n-1}^2),
\] 
where $|\epsilon_{n-1}| = n-1$.
Since $\UU_1 (H^*(S^{n-1}) \otimes \fg)$ is manifestly equivalent to the dg algebra~$U(\fg \otimes R_n)$,
we find that 
\[
\int_{S^{n-1}}\UU_n\fg \simeq U(\fg \otimes R_n)
\]
as $E_1$ algebras.
Recall as well that $\UU_n \fg$ is quasi-isomorphic to $\Sym(\fg[1-n])$ as cochain complexes.

@@

We also know that for an abelian dg Lie algebra~${\frak a}$, 
\[
\cliels({\frak a}) = \Sym({\frak a}[1])
\]
and hence provides a free dg commutative algebra.
This feature can be leveraged to prove the following result about $\EE_n$ centers of free commutative algebras.

@@

The universal property of centralizer (recall definition~\ref{D:centralizer}) implies that 
for any maps $A\stackrel{f}\to B$ and $B\stackrel{g}\to C$ of $\EE_n$ algebras, 
there is a natural map of $\EE_n$ algebras
\begin{equation}
\label{eqdef:canonicaltocentralizers} 
{\frak Z}_n(g) \otimes {\frak Z}_n(f) \longrightarrow {\frak Z}_n(g\circ f)
\end{equation}
that arises from following commutative diagram of $\EE_n$ algebras:
\[
\begin{tikzcd}
&   {\frak Z}_n(g) \otimes  {\frak Z}_n(f) \otimes A \arrow[rr, "\id\otimes \ev_f"] &&  {\frak Z}_n(g) \otimes  B \arrow[dr, "\ev_g"]\\
A \arrow[ur, "1\otimes \id_A"] \arrow[rr, "f"] && B \arrow[rr, "g"] \arrow[ur, "1\otimes \id_B"] && C 
\end{tikzcd}.
\]
When $f=g=\id_A:A\to A$, we thus obtain a canonical morphism 
\begin{equation} 
\label{eq:dgAssofcenter}
{\frak Z}_n(A){\otimes} {\frak Z}_n(A) \longrightarrow {\frak Z}_n(A).
\end{equation}
Lurie \cite{HA} has proved that this multiplication makes the center into an $E_1$ algebra in $\EE_n$ algebras 
and therefore an $E_{n+1}$-algebra, by Dunn additivity. 
%To be precise, there is the following result.
%
%\begin{prp}[\cite{LurieHA} Section 5] 
%\label{P:PtyCenter}
%\begin{itemize}
% \item The canonical map~\eqref{eq:dgAssofcenter} makes the center ${\frak Z}_n(A)$ into an $E_1$-algebra in the symmetric monoidal category of 
% $\EE_n$-algebras.
% \item There is a canonical equivalence of the $\infty$-category $E_1\mathrm{-Alg}(\EE_n\mathrm{-Alg})$ with $E_{n+1}\mathrm{-Alg}$.
%\end{itemize}
%\end{prp}

@@

The $\EE_n$ center ${\frak Z}_n(A)$ of an $\EE_n$ algebra $A$ is a rich object 
and controls how other algebras can act on $A$ as an $\EE_n$ algebra.
In a precise sense that we will discuss below, 
it is the {\em universal} $\EE_{n+1}$-algebra that acts on $A$ {\em qua} $\EE_n$ algebra.

As a familiar example, consider the degenerate situation of an $\EE_0$ algebra $V$, 
which is simply a cochain complex with a cochain map $k \to V$.
The $\EE_0$ center ${\frak Z}_0(V)$ is then $\End^\bullet(V)$,
the dg associative algebra that controls all actions of algebras on~$V$:
an action of an algebra $A$ on $V$ is equivalent to giving an algebra map $A \to \End^\bullet(V)$.
As another example, the $\EE_1$ center of a dg associative algebra $A$ is modeled by the Hochschild cochains $\Hoch^\bullet(A,A)$,
which is an $\EE_2$ algebra by Deligne's conjecture and which controls actions of $\EE_2$ algebras on~$A$.

Our model for $\EE_n$ centers of enveloping $\EE_n$ algebras provides useful insight into the behavior of centers and into how they interact with factorization homology.

Before we explore consequence of our results,
we review some key results about $\EE_n$ centers and how they act.
In Section \ref{sec:swiss} below, we will recall an elegant operadic articulation of how an $\EE_{n+1}$ algebra can act on an $\EE_n$ algebra 
and then we rephrase it in terms of {\em constructible factorization algebras} on a half-space~$\HH^{n+1}$. 
\owen{Mention lots of prior work, e.g., Greg et al, Ayala-Francis, Geoffroy Horel, and so on}.

@@

The operad of little $n$-disks is built from configurations of disjoint unions of $n$-disks inside $n$-dimensional Euclidean space.
The $(n+1)$-dimensional Swiss cheese operad is a two-colored operad whose algebras include pairs $(B, M)$ where $B$ is an $\EE_{n+1}$-algebra, $M$ is an $\EE_n$ algebra, and where $M$ is a left-module for $B$.

@@

\begin{qtn}
Is the canonical map \eqref{eqn: can cen int} a weak equivalence when $\UU_n \fg$ is replaced by an arbitrary $\EE_n$ algebra?
\end{qtn}

Even in the classical setting of associative algebras, it seems \dots

\owen{For all the associative algebras I tried, it seemed like this way true, but I only tried a very short list ...}

@@

In the case $k = 0$, we have the immediate corollary that
\[
\int_{S} \fZ_n(\fg) \simeq \fZ_0 \left( \int_S \UU_n \fg \right) ,
\]
which unwinds to 
\[
\clies(\fg \otimes \Omega^*(S), \cliels(\fg \otimes \Omega^*(S)) \simeq \End^\bullet(\cliels(\fg \otimes \Omega^*(S))),
\]
which looks rather tautological.
Nonetheless, by using other models for factorization homology,
one obtains less obvious identifications.

Consider first the case $n=1$ and $B = U \fg$. 
A classic result of \cite{HochSerre} is that the Hochschild cohomology of $U \fg$ can be expressed in terms of Lie algebra cohomology as 
\[
\Hoch^*(U\fg,U\fg) \simeq \clies(\fg, U\fg^{ad}).
\] 
On the right-hand side, we take the Chevalley--Eilenberg cochain complex with values in the module $U \fg$ equipped with the adjoint action.
The algebra structure is given by a special case of the convolution product as in Section~\ref{??}.

On the other hand, our model for the derived center ${\frak Z}(U(\fg))$ of $U \fg$ is the one-dimensional factorization algebra assigning the cochain complex
\[
\clies(\fg \otimes \Omega^*(U), \cliels( \fg \otimes \Omega^*_c(U)))
\]
to each open set $U \subset \RR$.
In the case that $U$ is an interval, this cochain complex is quasi-isomorphic to $\clies (\fg , U\fg^{ad})$.
Furthermore, one can verify that the resulting $E_1$-algebra structure agrees with the one coming from convolution.

Our model also gives us a simple description of the factorization homology of the derived center along the circle~$S^1$:
\begin{align*}
\Hoch_*(\Hoch^*(U \fg, U\fg)) 
&\simeq \int_{S^1} {\frak Z}(U(\fg)) \\
&\simeq \clies(\fg[\epsilon], \cliels( \fg[\epsilon])),
\end{align*}
where $\epsilon$ is a formal variable of degree~$1$. 
In the last step we use the fact that the circle is formal as a rational space.
\brian{We should compare with Tamarkin-Tsygan's noncommutative calculus (cf. section 2.6).
We could exhibit Theorem 2.7.1 explicitly in this case for the $\EE_n$ case with enveloping algebras.}

\owen{Other manifolds? Products of circles? Spheres?}

@@

\section{Centers and topological field theories}
\label{sec: TFT}
%
%Given an $E_{n+1}$-algebra one can speak of its $\infty$-category of left (or right) modules.
%This is obtained by ``forgetting" the $E_{n+1}$-algebra to an $E_1$-algebra then considering the left-modules for this $E_1$-algebra.
%
%The $\EE_n$ center, or $\EE_n$ Hochschild cohomology, of an $\EE_n$-algebra $A$ is the {\em universal} $E_{n+1}$-algebra which acts on $A$. 
%In Section \ref{sec:swiss} below, we will recall an elegant operadic interpretation of this universal picture and interpret it in terms of {\em constructible factorization algebras}. 
%In the case of $\EE_n$-enveloping algebras, we will provide a strict factorization model of this universal situation in terms of a constructible factorization algebra on an $(n+1)$-dimensional 
%manifold with boundary. 
%
%We will furthermore provide an interpretation of this constructible factorization algebra in terms of the quantization of a certain topological field theory. 
%The key insight is that there is a {\em classical limit} of the $\EE_n$-center $\fZ_n(\fg)$ which is equivalent to the observables of an $(n+1)$-dimensional topological field theory known as {\em BF theory}. 
%Likewise, there is a classical limit of $\UU_n(\fg)$ which can be viewed as a boundary condition for BF theory.
%
%In this sense, topological BF theory is the universal $(n+1)$-dimensional field theory which has the $\EE_n$-enveloping algebra as a boundary condition. 
%This partially confirms the terminology used in \cite{ButsonYoo}  of topological BF theory as the ``universal bulk theory" of $\UU_n(\fg)$.

In this section, we turn to an interpretation of the $\EE_n$ center of an $\EE_n$ enveloping algebra in terms of a certain topological field theory (TFT).

Given an $\EE_n$ algebra $A$, the pair $(\fZ_n (A) , A)$ is an algebra over the $(n+1)$-dimensional Swiss cheese operad. 
The first objective is to define a certain ``classical limit" of this pair in the case that $A$ is an $\EE_n$ enveloping algebra.

@@

The key insight is that there exists a filtration on our model $\bZ_n(\fg)$ for the $\EE_n$ center and our model $\bU_n (\fg)$ for the $\EE_n$ enveloping algebra  whose associated graded factorization algebras ${\rm Gr} \; \bZ_n(\fg)$ and ${\rm Gr} \; \bU_n(\fg)$ are commutative factorization algebras.

Given a filtered associative algebra whose associated graded is commutative, there exists a Poisson bracket on the associated graded algebra. 
If the associated graded of a filtered $\EE_n$ algebra is commutative, then it carries the structure of a $\PP_n$-algebra, which is similar to a Poisson algebra except the bracket is of cohomological degree $1-n$. 
There is a similar description of the ``classical limit"  of algebras over the $(n+1)$-dimensional Swiss cheese operad in terms of algebras over a certain two-colored operad $\PP_{[n+1,n]}$, introduced by Safronov \cite{Pavel1, Pavel2}, whose definition we recall below.

@@

In the previous section, we mentioned another geometric model for algebras over the $(n+1)$-dimensional Swiss cheese operad in terms of constructible factorization algebras on $(n+1)$-manifolds with boundary.
One drawback of the previous section is that we did not provide a model of this type for the $\EE_n$ center of an enveloping algebra. 
The next goal of this section is to provide a model of the classical limit of the $\EE_n$ center as a constructible factorization algebra.

@@

%Let $\fg$ be a dg Lie algebra and consider the $\EE_n$ algebra $\UU_n \fg$. 
%We have shown that a model for the $\EE_n$ center ${\frak Z}_n (\UU_n \fg) = {\frak Z}_n ({\rm id}_{\UU_n \fg})$ is the $n$-dimensional locally constant factorization algebra 
%\[
%\clie \left( \fg \otimes \Omega \; , \; \clieu (\fg \otimes \Omega_c) \right)  .
%\]

@@

We prove Proposition \ref{prp:swiss1} by exhibiting a filtration at the level of strict factorization algebras in our model of the $\EE_n$ center.

@@

Consider our factorization model for the $\EE_n$ enveloping algebra $\bU_n(\fg) = \cliels (\fg \otimes \Omega^\bu_c)$. 
The filtration on Chevalley--Eilenberg chains equips $\bU_n(\fg)$ with a filtration as a factorization algebra.

There is a similar filtration on our model for the $\EE_n$ center $\bZ_n(\fg)$ defined by
\[
F^k \bZ_n(\fg) = \clies \bigg(\fg \otimes \Omega \; , \; \clieu_{\leq k} (\fg \otimes \Omega_c) \bigg) .
\]

@@

We turn towards a model for the $\EE_n$ center as a constructible factorization algebra.

@@

In this section, we describe a relationship between our model of the $\EE_n$ center and a certain topological field theory. 
This theory admits a natural description via the AKSZ formalism \cite{AKSZ}, which we briefly recount now.

@@

The main result of this section is that the classical observables are equivalent to our constructible model for the classical limit of the $\EE_n$ center.

@@

\def \Fac {\mathrm{Fac}}
We now need to express the $\EE_n$ structure on ${\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n\fg}}(\UU_n \fg, B_f)$ induced by the equivalence of Proposition~\ref{P:ModentoModSn}, and then on the subsequent isomorphic hom spaces of modules morphisms.  Since we are going to take advantage of the factorization algebra presentation of $\UU_n( \fg)$, see~Theorem~\ref{T:UnofLie}, we recall the following factorization algebra description of the centralizer.
Let $\cA \stackrel{f}\to \cB$ be a morphism of locally constant factorization algebras on $\RR^n$ corresponding to an $\EE_n$ algebra map similarly denoted. Then by Theorems~\ref{thm:lurie1}, \ref{T:centralizer=inthom} the centralizer of $f$ is represented by the locally constant factorization algebra  
${\rm Mor}_{\Fac_{\cA}}(\cA, \cB_f)$ which is the internal mapping object  of maps from $\cA$ to $\cB_f$ in the $\infty$-category of locally constant factorization algebras on $\RR^n$ which are a $\cA$-module.
